---
title: "P8105_HW5"
author: Yijia Chen
date: 2021-11-20
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```
 
# Problem 1
clean the data

```{r}
homicide_df = 
  read.csv("data/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )
    ) %>% 
  relocate(city_state) %>% 
  filter(city_state != "PA40.461945") %>% 
  filter(city_state != "TulsaAL")
```

Lets focus on Baltimore

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test = 
  prop.test(
  x = baltimore_summary %>% pull(unsolved),
  n = baltimore_summary %>% pull(n)
)

baltimore_test %>% 
  broom::tidy()
```


Let's try to iterate across cities

first off, write a function and test it on few sample city

```{r}
prop_test_function = function(city_df) {
  
  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )

  city_test = 
    prop.test(
     x = city_summary %>% pull(unsolved),
     n = city_summary %>% pull(n)
    )
  return(city_test)
  
}

prop_test_function(baltimore_df)

homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()


```

now, lets iterate across all cities

```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))



```

try to make a plot showing estimates and confidence intervals

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


# Problem 2
Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time

Create read_csv function.

```{r}
file_base = "./data/hw5_data/"

read_function = function(file) {
  
  arm_data = 
    file_name = str_c(file_base, file)
    read_csv(file_name) %>% 
    pivot_longer(
      week_1:week_8,
      names_to = "week",
      names_prefix = "week_",
      values_to = "observation"
    )
  
}
```

1. Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe.

2. Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

```{r, warning = FALSE}
arm_df = 
  tibble(
    name = list.files("./data/hw5_data/")
    ) %>% 
  mutate(
    data = map(name, read_function)
  ) 

arm_df %>% 
  unnest(data) %>% 
  mutate(
    week = as.numeric(week),
    id = str_remove(name, ".csv"),
    arm_type = case_when(str_detect(name, "con") ~ "control",
                         str_detect(name, "exp") ~ "experimental")
  ) %>% 
  select(-name) %>% 
  relocate(id, arm_type) %>% 
  ggplot(aes(x = week, y = observation, color = id)) +
  geom_line() +
  facet_grid(. ~ arm_type) +
  labs(
    title = "Observations on Each Subject Over Time",
    y = "Observation",
    x = "Week"
  )
```
Overall, the experimental group has a higher value for observation than control group. Also, the values of observation for experimental group show a increasing trend from week 1 to week 8. The values of observation for control group do not show evident increased or decreased trend from week 1 to week 8.


# Problem 3
Load the "iris" dataset 

```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

1. For numeric variables, you should fill in missing values with the mean of non-missing values.

2. For character variables, you should fill in missing values with "virginica".


```{r}
fill_in_missing = function(vector) {
  
  if (is.numeric(vector)) {
    vector = ifelse(is.na(vector), mean(vector, na.rm = TRUE), vector)
  }
  
  if (is.character(vector)) {
    vector = ifelse(is.na(vector), "virginica", vector)
  }
  
  return(vector)
  
}

iris_fillin = 
  map(iris_with_missing, fill_in_missing) %>% 
  as_tibble()


table(is.na(iris_fillin))

```




